

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\exhyphenpenalty=10000

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

        \cventry
          {WEX Health} % Organization
          {Software Development Engineer} % Job title
          {} % Location
          {Jul. 2023 - Aug. 2024} % Date(s)
          {
            \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Engineered iOS applications with Swift and Objective-C; enhanced user engagement by 15\% using efficient MVC and MVVM patterns.}
    \item {Increased code coverage by 35\% via unit tests; this cut critical CI/CD errors by 40\%, strengthening code stability and build confidence.}
    \item {Streamlined integration and deployment processes using Azure and various collaboration tools, reducing integration time by 15\% and fostering teamwork.}
    \item {Drove API integrations with Visa for PCI compliance, significantly enhancing the security and scalability of mobile platforms through robust development.}
            \end{cvitems}
          }

        \cventry
          {WEX Health} % Organization
          {Software Engineer Intern} % Job title
          {} % Location
          {Sep. 2022 - Jul. 2023} % Date(s)
          {
            \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed a test automation suite in Python and Selenium, cutting manual testing time by 30\% while enhancing software reliability and performance.}
    \item {Developed C\# scripts for bug identification in analytics portals, ensuring robust data integrity and functionality for client-facing applications.}
    \item {Led initiatives within Agile/SCRUM teams to accelerate release cycles, demonstrating adaptability to rapidly changing business expectations.}
    \item {Implemented robust validation processes, achieving 99\% accuracy in SQL stored procedure outputs, crucial for data-dependent functionalities.}
            \end{cvitems}
          }

        \cventry
          {United States Army} % Organization
          {Base Expeditionary Targeting and Surveillance Systems Operator and Team Leader} % Job title
          {} % Location
          {Apr. 2014 - Apr. 2020} % Date(s)
          {
            \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Led tactical surveillance operations while integrating ISR software to provide real-time intelligence; utilized data effectively to improve decision-making.}
    \item {Automated processes using RAID system sensors for enhanced intelligence gathering, showcasing innovation in data management during operational missions.}
    \item {Managed intricate data workflows for surveillance systems, ensuring tactical decisions were informed by real-time data analysis for mission success.}
    \item {Honored with the Army Achievement Medal for exemplary leadership and analytical performance, reflecting capacity to handle complex operational scenarios.}
            \end{cvitems}
          }
\end{cventries}
